Models of lens candidates from Space Warps CFHTLS

### 2017-03-20 parts/massmodel.tex
remove endinput

Figure~\ref{fig:arriv} shows arrival-time surfaces corresponding to
the spaghetti diagrams in Figure~\ref{fig:splinput}.  The arrival-time
contours look like a machine-made elaborations of the input spaghetti
diagrams.  If the saddle-point contours in the arrival time are
qualitatively the same as the curves in the spaghetti diagram (the
detailed shape of the spaghetti curves is unimportant), it immediately
suggests a successful model.  On the other hand, if the arrival-time
surface has unexpected minima or saddle points, and especially if the
unexpected features are far from identified lens images, that signals
a doubtful model.  Figure~\ref{fig:synth} shows what we call synthetic
images, meaning reconstructions of the extended lensed features by
fitting for a source.  These were generated by a new method, explained
in Appendix~\ref{subsec:sourcefit}, implemented in offline
post-processing after the modelling process was complete.  The
synthetic images provided by SpaghettiLens during the collaborative
modelling and discussion were more crude; these are included in the
online supplement.

The arrival-time surface and synthetic image are summarised by one
diagnostic, the most important of all: are the lensed features
satisfactorily reproduced?  This diagnostic remains a judgment call by
modellers.  A useful quantitative criterion for whether the synthetic
image is consistent with the data would need to allow for PSF
dependence and unmodelled substructure ---otherwise all models would
be summarily rejected--- and it is not clear how to do this.

>>>>

Figure~\ref{fig:arriv} shows arrival-time surfaces corresponding to
the spaghetti diagrams in Figure~\ref{fig:splinput}.  The arrival-time
contours look like a machine-made elaborations of the input spaghetti
diagrams.  If the saddle-point contours in the arrival time are
qualitatively the same as the curves in the spaghetti diagram (the
detailed shape of the spaghetti curves is unimportant), it immediately
suggests a successful model.  On the other hand, if the arrival-time
surface has unexpected minima or saddle points, and especially if the
unexpected features are far from identified lens images, that signals
a doubtful model.  Figure~\ref{fig:synth} shows what we call synthetic
images, meaning reconstructions of the extended lensed features by
fitting for a source.  These were generated by new method, explained
in Appendix~\ref{subsec:sourcefit}, implemented in offline
post-processing after the modelling process was complete.  The
synthetic images provided by SpaghettiLens during the collaborative
modelling and discussion were more crude; these are included in the
online supplement.

The arrival-time surface and synthetic image are summarised by one
diagnostic, the most important of all: are the lensed features
satisfactorily repoduced?  This diagnostic remains a judgement call by
modellers.  A useful quantitative criterion for whether the synthetic
image is consistent with the data would need to allow for PSF
dependence and unmodelled substructure ---otherwise all models would
be summarily rejected--- and it is not clear how to do this.
